\section*{Acknowledgments}
\addcontentsline{toc}{section}{Acknowledgments}

I would like to thank my professor, George Vouros, for his invaluable support and guidance throughout the process of writing this thesis. His insights and feedback have been incredibly helpful and inspiring. I am especially grateful for the opportunity to collaborate with him on a paper, built upon this research, which we have submitted to the 24th International Conference on Agents and Multi-Agent Systems \href{https://aamas2025.org/}{(AAMAS 2025)}. Working together on this paper has been a truly rewarding experience. I look forward to many more collaborations in the future.\tinydouble

\noindent
A heartfelt thank you goes to my colleagues at NCSR "Demokritos", and especially my boss, Stasinos Konstantopoulos, for his constant patience and support. Balancing my work responsibilities with my master’s studies was challenging, but their understanding made it possible for me to manage both. While our work projects were not directly related to my thesis, the experience I gained was invaluable. It enhanced my research skills, refined my writing, and strengthened my technical abilities, all of which were crucial for completing this thesis.\tinydouble

\noindent
I would also like to thank my wonderful piano professor at Athens Conservatoire, Theodore Tzovanakis. Throughout this year, he has been an incredible source of emotional and mental support. Music has always been a big part of my life, helping me clear my mind and get inspired. They say inspiration comes from unexpected places, and for me, it comes from my deep love for music. A big thank you for all the beautiful moments we've shared together.\tinydouble

\noindent
Finally, I am deeply grateful to my parents, George and Foteini, for their unconditional love and support. They cared for me not only physically but also emotionally, creating a nurturing environment that allowed me to focus on my work and studies. Whether helping with housework when I was overwhelmed or encouraging me when I felt defeated, they always believed in me and stood by my side. Even during difficult times, they did everything they could to keep the stress away, making sure I stayed commited to my goals. Their strength and encouragement helped me stand back up when I stumbled, and keep pushing forward, even when giving up felt easier. Thank you mom and dad!\tinydouble

\noindent
Any opinions, findings, conclusions or recommendations expressed in this material are those of the author and do not necessarily reflect the views of the «funding body» or the view of University of Piraeus and Institute of Informatics \& Telecommunications of NCSR “Demokritos”. 