\section{Literature Study}

\begin{flushleft}

    This section forms the main body of my thesis, where I aim to provide a detailed explanation of the relative paper's content. Although much of the material is based on our paper, this section is included to offer a clear breakdown of our research work.\\~\\

    The first section introduces the key concepts of \emph{Game Theory and Analysis} used in our work, with a focus on dynamic games. The second section presents the \emph{Graph Coloring Game}, which serves as the basis for our analysis. Here, we explain the game's state and action spaces, as well as its reward system. In the third section, we present the \emph{$\alpha$-Rank}, the core evolutionary approach behind our methodology. This section provides a more detailed definition of \emph{Markov-Conley Chains} and how they model strategy evolution. Section four defines the problem we aim to solve and outlines our proposed methodology. Section five applies this methodology to the Graph Coloring Game, demonstrating how it can be implemented in practice. This section is further divided into subsections, which break down the methodology into clear steps. Finally, the conclusion summarizes our findings and suggests potential directions for future work.

\end{flushleft}

\newpage
\input{sections/section1}

\newpage
\input{sections/section2}

\newpage
\input{sections/section3}

\newpage
\input{sections/section4}

\newpage
\input{sections/section5}

\newpage
\input{sections/conclusion}

\newpage